Analysis Stand Features 

### 2018-11-12 analysis/analysis_stand_features.Rmd
update analisis stand features

---
title: "Analysis Stand Features "
author: "AJ Perez-Luque (@ajpelu)"
date: "2018 Jan"
output:  pdf_document
bibliography: references.bib 
csl: ecology.csl
---

@@

```{r, warning=FALSE, message=FALSE, echo=FALSE}
library("tidyverse")
library("raster")
library("stringr")
library('rgdal')
library("sp")
library("knitr")
library("broom")
library("multcomp")
library("pander")
library("devtools")
source_gist("https://gist.github.com/ajpelu/194e721077ec045a2b864088908e7aca", filename = 'table_glht.r') # multicomp table
```

# Prepare Data
```{r, echo=FALSE}
machine <- 'ajpelu'
# machine <- 'ajpeluLap'
di <- paste0('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep='')

# Read tree data
tree <- read.csv(file=paste0(di, '/data_raw/dendro_competence.csv'), header=TRUE, sep=',')

# Read spatial data 
# Centroid of focal tree 
## filename 
mygpx_ca <- paste0(di, 'data_raw/geoinfo/dendro_ca.GPX')
mygpx_sj <- paste0(di, 'data_raw/geoinfo/dendro_sj.GPX')

## reading  
field_work_ca <- readOGR(mygpx_ca, layer="waypoints", verbose = FALSE)
field_work_sj <- readOGR(mygpx_sj, layer="waypoints", verbose = FALSE)
```

@@

* Read data 
```{r, echo=FALSE}
# Read competition
compe <- read.csv(file=paste(di, "/data/competence/competence_indices.csv", sep=""), header=TRUE, sep=',')

@@

  out <- get(paste0('aov_', i))
  file_out <- file(paste0(di,'out/anovas_competition/aov_', i, '.txt'), "w")
  sink(file_out)
  cat("MODEL \n")
  print(out$mymodel) 
  cat("\n")

@@

tm <- s$tm

@@

* Read data 
```{r}
# Read topo data 
topo <- read.csv(file=paste(di, "/data/topo/topo.csv", sep=""), header=TRUE, sep=',')

@@

  file_out <- file(paste0(di,'out/anovas_topo/aov_', i, '.txt'), "w")
  sink(file_out)

@@

  file_out <- file(paste0(di,'out/anovas_ft/aov_', i, '.txt'), "w")
  sink(file_out)

@@

# Export data 
write.csv(stand_biotic, file=paste(di, "data/competence/biotic_stand_features.csv", sep=""), row.names = FALSE)

@@

# Export data 
# write.csv(out4, file=paste(di, "data/proto_tables/site_features.csv", sep=""), row.names = FALSE)
write.csv(out4, file=paste(di, "data/competence/resumen_medias_indices_competencia.csv", sep=""), row.names = FALSE)

@@

```{r}
topo_site <- topo %>% group_by(site) %>% summarise(
  elev_mean = mean(mde), 
  elev_min = min(mde), 
  elev_max = max(mde), 
  slope_mean = mean(slope)
)

@@

write.csv(site_general, file=paste(di, "data/sites_summary/site_general.csv", sep=""), row.names = FALSE)
```

>>>>

---
title: "Analysis Stand Features "
author: "AJ Perez-Luque (@ajpelu)"
date: "2018 Jan"
output:  
  md_document:
    toc: true
    variant: markdown_github
bibliography: ../refs/references.bib
csl: ../refs/ecology.csl
---

@@

```{r, warning=FALSE, message=FALSE, echo=FALSE}
library("here")
library("tidyverse")
library("raster")
library("stringr")
library('rgdal')
library("sp")
library("knitr")
library("broom")
library("multcomp")
library("pander")
library("devtools")
source_gist("https://gist.github.com/ajpelu/194e721077ec045a2b864088908e7aca", filename = 'table_glht.r') # multicomp table
```

# Prepare Data
```{r, echo=FALSE}
# machine <- 'ajpelu'
# # machine <- 'ajpeluLap'
# di <- paste0('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep='')

# Read tree data
tree <- read.csv(file=here::here('/data_raw/', 'dendro_competence.csv'), header=TRUE, sep=',')

# Read spatial data 
# Centroid of focal tree 
field_work_ca <- readOGR(here::here("/data_raw/geoinfo","dendro_ca.GPX" ), layer="waypoints", verbose = FALSE)
field_work_sj <- readOGR(here::here("/data_raw/geoinfo","dendro_sj.GPX" ), layer="waypoints", verbose = FALSE)
```

@@

* Read data 
```{r, echo=FALSE}
# Read competition
compe <- read.csv(here::here("/data/competence", "competence_indices.csv"), header=TRUE, sep=',')

@@

  out <- get(paste0('aov_', i))
  file_out <- file(here::here("out/anovas_competition", paste0("aov_", i, ".txt")), "w")
  sink(file_out)
  cat("MODEL \n")
  print(out$mymodel) 
  cat("\n")

@@

tm <- s$tm %>% as.data.frame()

@@

* Read data 
```{r}
# Read topo data 
topo <- read.csv(file=here::here("/data/topo", "topo.csv"), header=TRUE, sep=',')

@@

  file_out <- file(here::here("/out/anovas_topo", paste0("aov_", i, ".txt")), "w")
  sink(file_out)

@@

  file_out <- file(here::here("out/anovas_ft", paste0("aov_", i, ".txt")), "w")
  sink(file_out)

@@

# Export data 
write.csv(stand_biotic, file=here::here("data/competence", "biotic_stand_features.csv"), row.names = FALSE)

@@

# Export data 
# write.csv(out4, file=paste(di, "data/proto_tables/site_features.csv", sep=""), row.names = FALSE)
write.csv(out4, file=here::here("data/competence","resumen_medias_indices_competencia.csv"), row.names = FALSE)

@@

```{r}
topo_site <- topo %>% group_by(site) %>% summarise(
  elev_mean = mean(mde), 
  elev_min = min(mde), 
  elev_max = max(mde), 
  elev_sd = sd(mde), 
  elev_se = sd(mde)/sqrt(n()),
  slope_mean = mean(slope), 
  slope_sd = sd(slope), 
  slope_se = sd(slope)/sqrt(n()),
)

@@

write.csv(site_general, file=here::here("data/sites_summary", "site_general.csv"), row.names = FALSE)
```
